`traveltime`: an R package to calculate walking and motorised travel time from user-specified locations

### 2025-01-24 paper/paper.qmd
minor fixes: - fix faulty example extent in `get_friction_surface` - typos in `ext_matrix` - tidy chunks in paper

```{r ttexample,  include=FALSE}
library(terra)
library(malariaAtlas)
library(tidyterra)

@@

```{r ttexample_image, echo=FALSE}
#| label: "fig-tt_healthcare"
#| fig-cap: "Existing surface of motorised travel time from healthcare facilities, exerpted to Cambodia (Weiss et al., 2020)"

>>>>

```{r ttexample,  include=FALSE}
library(terra)
library(malariaAtlas)

@@

```{r ttexample_image, echo=FALSE}
#| label: "fig-tt_healthcare"
#| fig-cap: "Existing surface of motorised travel time from healthcare facilities, exerpted to Cambodia (Weiss et al., 2020)"
library(ggplot2)
library(tidyterra)
